Exploratory data analysis

### 2021-07-21 slides/data_checking.Rmd

```{r}
j_recall %>% 
  mutate(acc_recall = as.integer(acc_recall),
         j_score = j_score - 0.5) %>% 
  lme4::lmer(resp_conf ~ acc_recall * j_score + (1 + acc_recall | subj_num), data = .) %>% 
  summary()
```

>>>>

```{r}
j_recall %>% 
  mutate(acc_recall = as.integer(acc_recall),
         # so 0.5 is centered
         j_score = j_score - 0.5) %>% 
  lme4::lmer(resp_conf ~ acc_recall * j_score + (1 + acc_recall | subj_num), data = .) %>% 
  summary()
```
